%-----------EXPERIENCE-----------%
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Vrize India}{Nov 2022 -- Present}
{Software Engineer}{}

%-----------Softphone Automation-----------%
\resumeProjectHeading
{\textbf{Softphone Automation} $|$ \emph{Dotnet 6, Angular, Azure Datafactory, MSSQL}}    {}
\resumeItemListStart
\resumeItem {Optimizing call distribution based on user-load by implementing User Voice Route
    Balancing for teams, revamping call distribution.}
\resumeItem{Enhancing error tracking and reduced downtime by integrating comprehensive error
    managing for all stored procedures.}
\resumeItemListEnd

%-----------Tax Identity Shield-----------%
\resumeProjectHeading
{\textbf{Tax Identity Shield} $|$ \emph{Dotnet 6, Angular, NgRx, Azure Function Apps, Azure Appservice, Azure AD, MSSQL}}    {}
\resumeItemListStart
\resumeItem {Constructing a user-friendly Support Tool facilitating swift View/Edit/Fix actions on
    Experion User Subscriptions, thereby enhancing support team efficiency.}
\resumeItem{Facilitating informed decision-making by integrating a Dashboard for business
    stakeholders to monitor user adoption and error.}
\resumeItemListEnd

%-----------Identity Access Management & Business Partner Management-----------%
\resumeProjectHeading
{\textbf{Identity Access Management \& Business Partner Management} $|$ \emph{Dotnet 6, Vue 3, Pinia, Kafka Stream, Azure AD, MSSQL}}    {}
\resumeItemListStart
\resumeItem {Integrating Trulioo service for authenticating vendor accounts in the onboarding flow,
    ensuring secure and reliable authentication processes}
\resumeItem{Deploying the Trulioo service for authenticating vendor accounts seamlessly
    within the onboarding flow, guaranteeing secure and dependable authentication
    processes.}
\resumeItem{Contributing to requirement analysis and designed scalable solutions for user
    experience, ensuring optimal functionality and usability.}
\resumeItemListEnd

\vspace{10pt}
\resumeSubheading
{Thoughtworks Ltd.}{Apr 2021 -- Nov 2022}
{Consultant Developer}{}

%-----------Ad Plan Manager-----------%
\resumeProjectHeading
{\textbf{Ad Plan Manager} $|$ \emph{Angular, NgRx, Spring Boot, MSSQL, K8s}}    {}
\resumeItemListStart
\resumeItem {Led complete revamp of application architecture and data model to improve performance
    and onboard more users.}
\resumeItem{Production support and ticket resolutions}
\resumeItem{Mentoring new teammates to deliver a better product}
\resumeItemListEnd

\vspace{10pt}
\resumeSubheading
{LTIMindtree Ltd.}{Oct 2018 -- Apr 2021}
{Senior Software Developer}{}

%-----------Trade Promotion Management-----------%
\resumeProjectHeading
{\textbf{Trade Promotion Management} $|$ \emph{Angular, NgRx, Spring Boot, MSSQL, K8s}}    {}
\resumeItemListStart
\resumeItem {Developed a KPI calculation engine to dynamically evaluate formulas.}
\resumeItem{Established a Tenant-Resolver system to deliver tenant-specific business logic,
    transforming the application into a Multi-Tenant SaaS, presently catering to 5+ tenants.}
\resumeItemListEnd

\resumeSubHeadingListEnd