%-----------Professinal Summary-----------%
\section{\textbf{Professional Summary}}
\begin{itemize}
      \small
      \setlength{\itemsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0pt}
      \item Responsible for interacting with business partners for understanding and analyzing requirements and suggesting solutions.
      \item Gained over \textbf{5+ years} of experience as a \textbf{Full Stack Software Developer} with expertise in
            application architecture enhancements and data model optimizations.
      \item Proficient in Microservices Architecture and skilled at leveraging technologies like \textbf{.Net Core, Angular, Azure, and MSSQL} to boost application performance and user experience.
      \item Skilled in implementing innovative solutions such as User Voice Route Balancing and
            comprehensive error managing to optimize call distribution and reduce downtime.
      \item Experienced in collaboration with multi-site global teams on \textbf{requirement analysis} and \textbf{designing scalable solutions}
            for user experience enhancement, ensuring maximum functionality and usability.
      \item Recognized for driving successful outcomes in \textbf{complex development projects}
            through a proactive and innovative approach, with a track record of delivering
            impactful solutions.
      \item Understanding of \textbf{software testing principles and practices} to ensure the delivery of
            high-quality, reliable software products.
      \item Strong documentation skills to create technical specifications, design documents, and
            other project-related documentation as needed.
      \item Competent to revamp changing project requirements, technologies, and priorities in
            a dynamic and fast-paced agile environment.
\end{itemize}